Laws for Creating Trust in the Blockchain Age

### 2017-09-18 tex/article.tex
Footcite after dot

PUF devices can also be utilized for identification purposes\footcite{vskoric2005robust}.
An authentication mechanism based on PUFs works as follows: imagine a bank that needs to identify customers.
For each customer, the bank produces a PUF device and stores an initial set of challenge-response pairs securely in their database.
Next, the device is given to the customer.
When the customer wishes to authenticate himself, he presents the device.
The bank, in possession of a set challenge-response pairs unique to this device, sends a random challenge to the hardware.
If the device provides a correct response, authentication is successful.
Since cloning or mathematical modelling of the device is non-trivial, this is a secure mechanism to deploy for authentication purposes.

>>>>

PUF devices can also be utilized for identification purposes.\footcite{vskoric2005robust}
An authentication mechanism based on PUFs works as follows: imagine a bank that needs to identify customers.
For each customer, the bank produces a PUF device and stores an initial set of challenge-response pairs securely in their database.
Next, the device is given to the customer.
When the customer wishes to authenticate himself, he presents the device.
The bank, in possession of a set challenge-response pairs unique to this device, sends a random challenge to the hardware.
If the device provides a correct response, authentication is successful.
Since cloning or mathematical modelling of the device is non-trivial, this is a secure mechanism to deploy for authentication purposes.
